Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-19 paper.tex
update

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. but there exists scalability problems for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

@@

\section{Motivation and Problem Description}\label{problemDes}

The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request. The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above. A motivating example of this problem is shown in Fig \ref{motivation}. The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning from a scholar who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city. The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.

@@

We herein formalise the assumptions and concepts utilised in our approach
which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$. This overall composition goal is demonstrated in two parts: functional part and non-functional part. The functional part is defined by given task inputs and desired task outputs. The nonfunctional part specifies overall QoS requirements. To accomplish the composition goal, two stages are involved, services discovery and service selection. Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$. If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$. To ensure the composition solution returns the desired $Comp.G$ that considers a higher degree of matching $O_{T}$ and a near-optimised $QoS_{T}$, We first demonstrate the concepts in both semantic matchmaking types and $QoS$ as follows, and then propose a quality model that take care of semantic matchmaking quality and QoS simultaneously in Sect. \ref{Comprehensive_Quality_Model}.

>>>>

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. but there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

@@

\section{Motivation and Problem Description}\label{problemDes}
\subsection{Motivation}\label{Motivation}

The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request. The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above. A motivating example of this problem is shown in Fig \ref{motivation}. The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem from scholars who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city. The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.

@@

\subsection{Problem Formulation}\label{Motivation}

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a weighted DAG composition model, and QoS calculation model.

\textbf{Semantic Web Service Model}. The semantic web service model represent web services with functional descriptions, and how interoperability of web services enable matchmaking to automatically generate composition solutions.

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving task inputs $I_{T}$ and expecting desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are linked to the concepts $C$ in an ontology $O = \{C, Taxonomy\}$.

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$

The nonfunctional part specifies overall QoS

 requirements. To accomplish the composition goal, two stages are involved, services discovery and service selection. Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$. If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$. To ensure the composition solution returns the desired $Comp.G$ that considers a higher degree of matching $O_{T}$ and a near-optimised $QoS_{T}$, We first demonstrate the concepts in both semantic matchmaking types and $QoS$ as follows, and then propose a quality model that take care of semantic matchmaking quality and QoS simultaneously in Sect. \ref{Comprehensive_Quality_Model}.
